\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-12-04 paper/mswp2012-proposal.tex
gantt

\pagebreak
\subsubsection{Range of Functions RF2}
\label{sect:workplan:phase1:rf2}
\textbf{Dependencies:} RF1 \ref{sect:workplan:phase1:rf1}, ES1 \ref{sect:workplan:phase1:es1}, ES2 \ref{sect:workplan:phase1:es2}\\
\textbf{Description:} Combine knowledge from the two empirical studies ES1 and ES2 and evaluate the brainstormed feature list. Check if the discovered features from the empirical studies are matching the created feature list\\
\textbf{Responsible person(s):} Research Team\\
\textbf{Goal(s) and expected Results:} Final set of features for version 1.0 (Milestone M1)\\

@@

\subsubsection{Evaluierung und Redesign ER3}
\label{sect:workplan:phase3:er3}
\textbf{Dependencies:} P3 \ref{sect:workplan:phase3:p3}, P4 \ref{sect:workplan:phase3:p4}\\
\textbf{Description:} Evaluate and redesign the system and mobile clients by the users with several iterations.\\
\textbf{Responsible person(s):} Dev Team, Users\\
\textbf{Goal(s) and expected Results:} Redesigned system and mobile clients (Version 2.0, Milestone M4)\\

>>>>

\pagebreak
\subsubsection{Range of Functions RF2}
\label{sect:workplan:phase1:rf2}
\textbf{Dependencies:} RF1 \ref{sect:workplan:phase1:rf1}, ES1 \ref{sect:workplan:phase1:es1}, ES2 \ref{sect:workplan:phase1:es2}\\
\textbf{Description:} Combine knowledge from the two empirical studies ES1 and ES2 and evaluate the brainstormed feature list. Check if the discovered features from the empirical studies are matching the created feature list\\
\textbf{Responsible person(s):} Research Team\\
\textbf{Goal(s) and expected Results:} Final set of features for version 0.1 (Milestone M1)\\

@@

\subsubsection{Evaluierung und Redesign ER3}
\label{sect:workplan:phase3:er3}
\textbf{Dependencies:} P3 \ref{sect:workplan:phase3:p3}, P4 \ref{sect:workplan:phase3:p4}\\
\textbf{Description:} Evaluate and redesign the system and mobile clients by the users with several iterations.\\
\textbf{Responsible person(s):} Dev Team, Users\\
\textbf{Goal(s) and expected Results:} Redesigned system and mobile clients (Version 1.0, Milestone M4)\\
